### 2020-01-31 ncov.tex
update
AUTO

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have prioritized estimating the basic reproductive number \Ro, defined as the average number of secondary cases caused by a primary case.
While these efforts are extremely valuable, their modeling approaches and the resulting estimates vary widely.
Here, we present a framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.
While rapid response during an outbreak is important, careful consideration of methodology is also important.
Modelers should work with field-workers to develop better methods for characterizing generation intervals.

@@

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have prioritized estimating the basic reproductive number \Ro, defined as the average number of secondary cases caused by a primary case.
While these efforts are extremely valuable, their modeling approaches and the resulting estimates vary widely.
Here, we present a framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.
While rapid response during an outbreak is important, careful consideration of methodology is also worthwhile.
Modelers should work with field-workers to develop better methods for characterizing generation intervals.

@@

There are other important phenomena not covered by our simple framework. Examples that seem relevant to this outbreak include: changing reporting rates, changing generation intervals, and reporting delays (including the effects of weekends and holidays.)
\jd{This \P\ should be fleshed out and citated.}
